---
title: "Analyzing performance of cricketers and cricket teams with cricketr templates"
author: "Tinniam V Ganesh"
date: "March 29, 2019"
output: html_document
---

This post includes a template which you can use for analyzing the performances of cricketers, both batsmen and bowlers in Test, ODI and Twenty 20 cricket. Additionally this template can also be used for analyzing performancs of teams in Test, ODI and T20  matches using my R package **cricketr**. To see actual usage of functions related to players in the R package cricketr see [Introducing cricketr! : An R package to analyze performances of cricketers](https://gigadom.in/2015/07/04/introducing-cricketr-a-r-package-to-analyze-performances-of-cricketers/) and associated posts on cricket in [Index of posts](https://gigadom.in/aa-2/). For the analyses on team performances see [https://gigadom.in/2019/06/21/cricpy-adds-team-analytics-to-its-repertoire/](https://gigadom.in/2019/06/21/cricpy-adds-team-analytics-to-its-repertoire/)

The 'cricketr'  package uses the statistics info available in [ESPN Cricinfo Statsguru](http://stats.espncricinfo.com/ci/engine/stats/index.html). The current version of this package supports all formats of the game including Test, ODI and
Twenty20 versions. 

You should be able to install the package from GitHub and use the many functions available in the package. Please mindful of the [ESPN Cricinfo Terms of Use](http://www.espncricinfo.com/ci/content/site/company/terms_use.html) 

Take a look at my short video tutorial on my R package cricketr on Youtube - [R package cricketr - A short tutorial](https://www.youtube.com/edit?o=U&video_id=q9uMPFVsXsI)

Do check out my interactive Shiny app implementation using the cricketr package - [Sixer - R package cricketr's new Shiny avatar](https://tvganesh.shinyapps.io/Sixer)

#The **cricketr** package
The cricketr package has several functions that perform several different analyses on both batsman and bowlers. The package can also analyze performances of teams The package has function that plot  percentage frequency runs or wickets, runs likelihood for a batsman, relative run/strike rates of batsman and relative performance/economy rate for bowlers are available. Other interesting functions include batting performance moving average, forecast  and a function to check whether the batsmans in in-form or out-of-form.

In addition performances of teams against different oppositions at different venues can be computed and plotted. The timeline of wins & losses can be plotted.

## A. Performances of batsmen and bowlers
The data for a particular player can be obtained with the getPlayerData() function. To do you will need to go to [ESPN CricInfo Player](http://www.espncricinfo.com/ci/content/player/index.html) and type in the name of the player for e.g Ricky Ponting, Sachin Tendulkar etc. This will bring up a page which have the profile number for the player e.g. for Sachin Tendulkar this would be http://www.espncricinfo.com/india/content/player/35320.html. Hence, Sachin's profile is 35320. This can be used to get the data for Tendulkar as shown below

The cricketr package is now available from **CRAN!!!** You should be able to install directly with

###1.  Install the cricketr package
```{r message=FALSE,warning=FALSE}
if (!require("cricketr")){
    install.packages("cricketr",lib = "c:/test")
}
library(cricketr)

```

The cricketr package includes some pre-packaged sample (.csv) files. You can use these sample to test functions  as shown below

```{r }
# Retrieve the file path of a data file installed with cricketr
#pathToFile <- system.file("data", "tendulkar.csv", package = "cricketr")
#batsman4s(pathToFile, "Sachin Tendulkar")

# The general format is pkg-function(pathToFile,par1,...)
#batsman4s(<path-To-File>,"Sachin Tendulkar")
```

```
The pre-packaged files can be accessed as shown above.
To get the data of any player use the function in Test, ODI and Twenty20 use the following

### 2.  For Test cricket

```{r}
#tendulkar <- getPlayerData(35320,dir="..",file="tendulkar.csv",type="batting",homeOrAway=c(1,2), result=c(1,2,4))

```

### 2a.  For ODI cricket

```{r}
#tendulkarOD <- getPlayerDataOD(35320,dir="..",file="tendulkarOD.csv",type="batting")

```

### 2b For Twenty 20 cricket
```{r}
#tendulkarT20 <- getPlayerDataTT(35320,dir="..",file="tendulkarT20.csv",type="batting")

```


**Important Note**
This needs to be done only once for a player. This function stores the player's data in a CSV file (for e.g. tendulkar.csv as above) which can then be reused for all other functions. Once we have the data for the players many analyses can be done. This post will use the stored CSV file obtained with a prior getPlayerData for all subsequent analyses

## Sachin Tendulkar's performance -  Basic Analyses
The 3 plots below provide the following for Tendulkar

1. Frequency percentage of runs in each run range over the whole career
2. Mean Strike Rate for runs scored in the given range
3. A histogram of runs frequency percentages in runs ranges
For example

###3. Basic analyses
```{r cache=TRUE}
par(mfrow=c(1,3))
par(mar=c(4,4,2,2))
#batsmanRunsFreqPerf("./tendulkar.csv","Tendulkar")
#batsmanMeanStrikeRate("./tendulkar.csv","Tendulkar")
#batsmanRunsRanges("./tendulkar.csv","Tendulkar")
dev.off()
```


1. Player 1
2. Player 2
3. Player 3
4. Player 4 

###4. More analyses
```{r }
par(mfrow=c(1,3))
par(mar=c(4,4,2,2))
#batsman4s("./player1.csv","Player1")
#batsman6s("./player1.csv","Player1")
#batsmanMeanStrikeRate("./player1.csv","Player1")

# For ODI and T20
#batsmanScoringRateODTT("./player1.csv","Player1")
dev.off()
```


```{r }
par(mfrow=c(1,3))
par(mar=c(4,4,2,2))
#batsman4s("./player2.csv","Player2")
#batsman6s("./player2.csv","Player2")
#batsmanMeanStrikeRate("./player2.csv","Player2")
# For ODI and T20
#batsmanScoringRateODTT("./player1.csv","Player1")
dev.off()
```


```{r  }
par(mfrow=c(1,3))
par(mar=c(4,4,2,2))
#batsman4s("./player3.csv","Player3")
#batsman6s("./player3.csv","Player3")
#batsmanMeanStrikeRate("./player3.csv","Player3")
# For ODI and T20
#batsmanScoringRateODTT("./player1.csv","Player1")

dev.off()
```

```{r plot4 }
par(mfrow=c(1,3))
par(mar=c(4,4,2,2))
#batsman4s("./player4.csv","Player4")
#batsman6s("./player4.csv","Player4")
#batsmanMeanStrikeRate("./player4.csv","Player4")
# For ODI and T20
#batsmanScoringRateODTT("./player1.csv","Player1")
dev.off()
```
*Note*: For mean strike rate in ODI and Twenty20 use the function batsmanScoringRateODTT()

###5.Boxplot histogram plot

This plot shows a combined boxplot of the Runs ranges  and a histogram of the Runs Frequency
```{r }
#batsmanPerfBoxHist("./player1.csv","Player1")
#batsmanPerfBoxHist("./player2.csv","Player2")
#batsmanPerfBoxHist("./player3.csv","Player3")
#batsmanPerfBoxHist("./player4.csv","Player4")

```



###6.  Contribution to won and lost matches


For the 2 functions below you will have to use the getPlayerDataSp() function. I 
have commented this as I already have these files. This function can only be used for Test matches
```{r}
#player1sp <- getPlayerDataSp(xxxx,tdir=".",tfile="player1sp.csv",ttype="batting")
#player2sp <- getPlayerDataSp(xxxx,tdir=".",tfile="player2sp.csv",ttype="batting")
#player3sp <- getPlayerDataSp(xxxx,tdir=".",tfile="player3sp.csv",ttype="batting")
#player4sp <- getPlayerDataSp(xxxx,tdir=".",tfile="player4sp.csv",ttype="batting")
```

```{r }
par(mfrow=c(2,2))
par(mar=c(4,4,2,2))
#batsmanContributionWonLost("player1sp.csv","Player1")
#batsmanContributionWonLost("player2sp.csv","Player2")
#batsmanContributionWonLost("player3sp.csv","Player3")
#batsmanContributionWonLost("player4sp.csv","Player4")
dev.off()

```

### 7, Performance at home and overseas
This function also requires the use of getPlayerDataSp() as shown above. This can only be used for Test matches
```{r }
par(mfrow=c(2,2))
par(mar=c(4,4,2,2))
#batsmanPerfHomeAway("player1sp.csv","Player1")
#batsmanPerfHomeAway("player2sp.csv","Player2")
#batsmanPerfHomeAway("player3sp.csv","Player3")
#batsmanPerfHomeAway("player4sp.csv","Player4")
dev.off()

```

###8.  Batsman average at different venues

```{r }
par(mfrow=c(2,2))
par(mar=c(4,4,2,2))
#batsmanAvgRunsGround("./player1.csv","Player1")
#batsmanAvgRunsGround("./player2.csv","Player2")
#batsmanAvgRunsGround("./player3.csv","Ponting")
#batsmanAvgRunsGround("./player4.csv","Player4")
dev.off()
```


###9. Batsman average against different opposition

```{r}
par(mfrow=c(2,2))
par(mar=c(4,4,2,2))
#batsmanAvgRunsOpposition("./player1.csv","Player1")
#batsmanAvgRunsOpposition("./player2.csv","Player2")
#batsmanAvgRunsOpposition("./player3.csv","Ponting")
#batsmanAvgRunsOpposition("./player4.csv","Player4")
dev.off()
```

###10. Runs Likelihood of batsman

```{r }
par(mfrow=c(2,2))
par(mar=c(4,4,2,2))
#batsmanRunsLikelihood("./player1.csv","Player1")
#batsmanRunsLikelihood("./player2.csv","Player2")
#batsmanRunsLikelihood("./player3.csv","Ponting")
#batsmanRunsLikelihood("./player4.csv","Player4")
dev.off()
```


###11. Moving Average of runs in career


```{r }
par(mfrow=c(2,2))
par(mar=c(4,4,2,2))
#batsmanMovingAverage("./player1.csv","Player1")
#batsmanMovingAverage("./player2.csv","Player2")
#batsmanMovingAverage("./player3.csv","Ponting")
#batsmanMovingAverage("./player4.csv","Player4")
dev.off()
```

###12. Cumulative Average runs of batsman in career
```{r }
par(mfrow=c(2,2))
par(mar=c(4,4,2,2))
#batsmanCumulativeAverageRuns("./player1.csv","Player1")
#batsmanCumulativeAverageRuns("./player2.csv","Player2")
#batsmanCumulativeAverageRuns("./player3.csv","Ponting")
#batsmanCumulativeAverageRuns("./player4.csv","Player4")
dev.off()
```

###13. Cumulative Average strike rate  of batsman in career
```{r }
par(mfrow=c(2,2))
par(mar=c(4,4,2,2))
#batsmanCumulativeStrikeRate("./player1.csv","Player1")
#batsmanCumulativeStrikeRate("./player2.csv","Player2")
#batsmanCumulativeStrikeRate("./player3.csv","Ponting")
#batsmanCumulativeStrikeRate("./player4.csv","Player4")
dev.off()
```

###14. Future Runs forecast 
Here are plots that forecast how the batsman will perform in future. In this case 90% of the career runs trend is uses as the training set. the remaining 10% is the test set. 

A Holt-Winters forecating model is used to forecast future performance based on the 90% training set. The forecated runs trend is plotted. The test set is also plotted to see how close the forecast and the actual matches

Take a look at the runs forecasted for the batsman below.

```{r}
par(mfrow=c(2,2))
par(mar=c(4,4,2,2))
#batsmanPerfForecast("./player1.csv","Player1")
#batsmanPerfForecast("./player2.csv","Player2")
#batsmanPerfForecast("./player3.csv","Player3")
#batsmanPerfForecast("./player4.csv","Player4")
dev.off()
```

###15. Relative Mean Strike Rate plot
The plot below compares the Mean Strike Rate of the batsman for each of the runs ranges of 10 and plots them. The plot indicate the following

```{r }
frames <- list("./player1.csv","./player2.csv","player3.csv","player4.csv")
names <- list("Player1","Player2","Player3","Player4")
#relativeBatsmanSR(frames,names)

```


###16. Relative Runs Frequency plot
The plot below gives the relative Runs Frequency Percetages for each 10 run bucket. The plot below show

```{r }
frames <- list("./player1.csv","./player2.csv","player3.csv","player4.csv")
names <- list("Player1","Player2","Player3","Player4")
#relativeRunsFreqPerf(frames,names)

```


###17. Relative cumulative average runs in career
```{r }
frames <- list("./player1.csv","./player2.csv","player3.csv","player4.csv")
names <- list("Player1","Player2","Player3","Player4")
#relativeBatsmanCumulativeAvgRuns(frames,names)

```


###18. Relative cumulative average strike rate in career
```{r }
frames <- list("./player1.csv","./player2.csv","player3.csv","player4.csv")
names <- list("Player1","Player2","Player3","player4")
#relativeBatsmanCumulativeStrikeRate(frames,names)

```


###19. Check Batsman In-Form or Out-of-Form
The below computation uses Null Hypothesis testing and p-value to determine if the batsman is in-form or out-of-form. For this 90% of the career runs is chosen as the population and the mean computed. The last 10% is chosen to be the sample set and the sample Mean and the sample Standard Deviation are caculated.

The Null Hypothesis (H0) assumes that the batsman continues to stay in-form where the sample mean is within 95% confidence interval of population mean
The Alternative (Ha) assumes that the batsman is out of form the sample mean is beyond the 95% confidence interval of the population mean.

A significance value of 0.05 is chosen and p-value us computed
If p-value >= .05 - Batsman In-Form
If p-value < 0.05 - Batsman Out-of-Form

**Note** Ideally the p-value should be done for a population that follows the Normal Distribution. But the runs population is usually left skewed. So some correction may be needed. I will revisit this later

This is done for the Top 4 batsman
```{r }
#checkBatsmanInForm("./player1.csv","Player1")
#checkBatsmanInForm("./player2.csv","Player2")
#checkBatsmanInForm("./player3.csv","Player3")
#checkBatsmanInForm("./player4.csv","Player4")

```

###20. 3D plot of Runs vs Balls Faced and Minutes at Crease
The plot is a scatter plot of Runs vs Balls faced and Minutes at Crease. A prediction plane is fitted

```{r plot16,cache=TRUE}
par(mfrow=c(1,2))
par(mar=c(4,4,2,2))
#battingPerf3d("./player1.csv","Player1")
#battingPerf3d("./player2.csv","Player2")
```

```{r plot17,cache=TRUE}
par(mfrow=c(1,2))
par(mar=c(4,4,2,2))
#battingPerf3d("./player3.csv","Player3")
#battingPerf3d("./player4.csv","player4")
dev.off()
```

###21. Predicting Runs given Balls Faced and Minutes at Crease
A multi-variate regression plane is fitted between Runs and Balls faced +Minutes at crease.
```{r messages=FALSE,cache=TRUE}
BF <- seq( 10, 400,length=15)
Mins <- seq(30,600,length=15)
newDF <- data.frame(BF,Mins)
#Player1 <- batsmanRunsPredict("./player1.csv","Player1",newdataframe=newDF)
#Player2 <- batsmanRunsPredict("./player2.csv","Player2",newdataframe=newDF)
#ponting <- batsmanRunsPredict("./player3.csv","Player3",newdataframe=newDF)
#sangakkara <- batsmanRunsPredict("./player4.csv","Player4",newdataframe=newDF)
```

```{r }
#batsmen <-cbind(round(Player1$Runs),round(Player2$Runs),round(Player3$Runs),round(Player4$Runs))
#colnames(batsmen) <- c("Player1","Player2","Player3","Player4")
#newDF <- data.frame(round(newDF$BF),round(newDF$Mins))
#colnames(newDF) <- c("BallsFaced","MinsAtCrease")
#predictedRuns <- cbind(newDF,batsmen)
#predictedRuns

```

# Analysis of bowlers

1. Bowler1
2. Bowler2
3. Bowler3
4. Bowler4

player1 <- getPlayerData(xxxx,dir="..",file="player1.csv",type="bowling")
*Note* For One day you will have to use getPlayerDataOD() and for Twenty20 it is getPlayerDataTT()

###21. Wicket Frequency Plot
This plot below computes the percentage frequency of number of wickets taken for e.g
1 wicket x%, 2 wickets y% etc and plots them as a continuous line 

```{r }
par(mfrow=c(1,3))
par(mar=c(4,4,2,2))
#bowlerWktsFreqPercent("./bowler1.csv","Bowler1")
#bowlerWktsFreqPercent("./bowler2.csv","Bowler2")
#bowlerWktsFreqPercent("./bowler3.csv","Bowler3")
dev.off()
```

###22. Wickets Runs plot

```{r }
par(mfrow=c(1,3))
par(mar=c(4,4,2,2))
#bowlerWktsRunsPlot("./bowler1.csv","Bowler1")
#bowlerWktsRunsPlot("./bowler2.csv","Bowler2")
#bowlerWktsRunsPlot("./bowler3.csv","Bowler3")
dev.off()
```

###23. Average wickets at different venues

```{r }
#bowlerAvgWktsGround("./bowler3.csv","Bowler3")

```

###24. Average wickets against different opposition

```{r }
#bowlerAvgWktsOpposition("./bowler3.csv","Bowler3")

```


###25. Wickets taken moving average

```{r }
par(mfrow=c(1,3))
par(mar=c(4,4,2,2))
#bowlerMovingAverage("./bowler1.csv","Bowler1")
#bowlerMovingAverage("./bowler2.csv","Bowler2")
#bowlerMovingAverage("./bowler3.csv","Bowler3")

dev.off()
```

###26. Cumulative Wickets taken 
```{r }
par(mfrow=c(1,3))
par(mar=c(4,4,2,2))
#bowlerCumulativeAvgWickets("./bowler1.csv","Bowler1")
#bowlerCumulativeAvgWickets("./bowler2.csv","Bowler2")
#bowlerCumulativeAvgWickets("./bowler3.csv","Bowler3")
dev.off()
```

###27. Cumulative Economy rate
```{r }
par(mfrow=c(1,3))
par(mar=c(4,4,2,2))
#bowlerCumulativeAvgEconRate("./bowler1.csv","Bowler1")
#bowlerCumulativeAvgEconRate("./bowler2.csv","Bowler2")
#bowlerCumulativeAvgEconRate("./bowler3.csv","Bowler3")
dev.off()
```

###28. Future Wickets forecast 
Here are plots that forecast how the bowler will perform in future. In this case 90% of the career wickets trend is used as the training set. the remaining 10% is the test set. 

A Holt-Winters forecating model is used to forecast future performance based on the 90% training set. The forecated wickets trend is plotted. The test set is also plotted to see how close the forecast and the actual matches


```{r }
par(mfrow=c(1,3))
par(mar=c(4,4,2,2))
#bowlerPerfForecast("./bowler1.csv","Bowler1")
#bowlerPerfForecast("./bowler2.csv","Bowler2")
#bowlerPerfForecast("./bowler3.csv","Bowler3")
dev.off()
```

###29. Contribution to matches won and lost
As discussed above the next 2 charts require the use of getPlayerDataSp(). This can only be done for Test matches
```{r}
#bowler1sp <- getPlayerDataSp(xxxx,tdir=".",tfile="bowler1sp.csv",ttype="bowling")
#bowler2sp <- getPlayerDataSp(xxxx,tdir=".",tfile="bowler2sp.csv",ttype="bowling")
#bowler3sp <- getPlayerDataSp(xxxx,tdir=".",tfile="bowler3sp.csv",ttype="bowling")
```


```{r }
par(mfrow=c(1,3))
par(mar=c(4,4,2,2))
#bowlerContributionWonLost("bowler1sp","Bowler1")
#bowlerContributionWonLost("bowler2sp","Bowler2")
#bowlerContributionWonLost("bowler3sp","Bowler3")
dev.off()
```

###30. Performance home and overseas.
This can only be done for Test matches
```{r }
par(mfrow=c(1,3))
par(mar=c(4,4,2,2))
#bowlerPerfHomeAway("bowler1sp","Bowler1")
#bowlerPerfHomeAway("bowler2sp","Bowler2")
#bowlerPerfHomeAway("bowler3sp","Bowler3")
dev.off()
```

###31 Relative Wickets Frequency Percentage


```{r }
frames <- list("./bowler1.csv","./bowler3.csv","bowler2.csv")
names <- list("Bowler1","Bowler3","Bowler2")
#relativeBowlingPerf(frames,names)
```

###32 Relative Economy Rate against wickets taken
```{r }
frames <- list("./bowler1.csv","./bowler3.csv","bowler2.csv")
names <- list("Bowler1","Bowler3","Bowler2")
#relativeBowlingER(frames,names)
```

###33 Relative cumulative average wickets of bowlers in career
```{r }
frames <- list("./bowler1.csv","./bowler3.csv","bowler2.csv")
names <- list("Bowler1","Bowler3","Bowler2")
#relativeBowlerCumulativeAvgWickets(frames,names)
```


###34 Relative cumulative average economy rate of bowlers

```{r }
frames <- list("./bowler1.csv","./bowler3.csv","bowler2.csv")
names <- list("Bowler1","Bowler3","Bowler2")
#relativeBowlerCumulativeAvgEconRate(frames,names)
```


###35 Check for bowler in-form/out-of-form
The below computation uses Null Hypothesis testing and p-value to determine if the bowler is in-form or out-of-form. For this 90% of the career wickets is chosen as the population and the mean computed. The last 10% is chosen to be the sample set and the sample Mean and the sample Standard Deviation are caculated.

The Null Hypothesis (H0) assumes that the bowler continues to stay in-form where the sample mean is within 95% confidence interval of population mean
The Alternative (Ha) assumes that the bowler is out of form the sample mean is beyond the 95% confidence interval of the population mean.

A significance value of 0.05 is chosen and p-value us computed
If p-value >= .05 - Batsman In-Form
If p-value < 0.05 - Batsman Out-of-Form

**Note** Ideally the p-value should be done for a population that follows the Normal Distribution. But the runs population is usually left skewed. So some correction may be needed. I will revisit this later

**Note:** The check for the form status of the bowlers indicate

```{r }
#checkBowlerInForm("./bowler1.csv","Bowler1")
#checkBowlerInForm("./bowler2.csv","Bowler2")
#checkBowlerInForm("./bowler3.csv","Bowler3")
dev.off()
```



##B. Performances of teams
The following functions will get the team data for Tests, ODI and T20s

###1a. Get Test team data
```{r}
#country1Test= getTeamDataHomeAway(dir=".",teamView="bat",matchType="Test",file="country1Test.csv",save=True,teamName="Country1")
#country2Test= getTeamDataHomeAway(dir=".",teamView="bat",matchType="Test",file="country2Test.csv",save=True,teamName="Country2")
#country3Test= getTeamDataHomeAway(dir=".",teamView="bat",matchType="Test",file="country3Test.csv",save=True,teamName="Country3")
```

###1b. Get ODI team  data
```{r}
#team1ODI=  getTeamDataHomeAway(dir=".",matchType="ODI",file="team1ODI.csv",save=True,teamName="team1")
#team2ODI=  getTeamDataHomeAway(dir=".",matchType="ODI",file="team2ODI.csv",save=True,teamName="team2")
#team3ODI=  getTeamDataHomeAway(dir=".",matchType="ODI",file="team3ODI.csv",save=True,teamName="team3")
```

###1c. Get T20 team  data
```{r}
#team1T20 = getTeamDataHomeAway(matchType="T20",file="team1T20.csv",save=True,teamName="team1")
#team2T20 = getTeamDataHomeAway(matchType="T20",file="team2T20.csv",save=True,teamName="team2")
#team3T20 = getTeamDataHomeAway(matchType="T20",file="team3T20.csv",save=True,teamName="team3")
```

###2a. Test - Analyzing test performances against opposition
```{r}
# Get the performance of Indian test team against all teams at all venues as a dataframe
#df <- teamWinLossStatusVsOpposition("country1Test.csv",teamName="Country1",opposition=c("all"),homeOrAway=c("all"),matchType="Test",plot=FALSE)
#head(df)

# Plot the performance of Country1 Test team  against all teams at all venues
#teamWinLossStatusVsOpposition("country1Test.csv",teamName="Country1",opposition=c("all"),homeOrAway=c("all"),matchType="Test",plot=TRUE)

# Plot the performance of Country1 Test team  against specific teams at home/away venues
#teamWinLossStatusVsOpposition("country1Test.csv",teamName="Country1",opposition=c("Country2","Country3","Country4"),homeOrAway=c("home","away","neutral"),matchType="Test",plot=TRUE)

```


###2b. Test - Analyzing test performances against opposition at different grounds
```{r}
# Get the performance of Indian test team against all teams at all venues as a dataframe
#df <- teamWinLossStatusAtGrounds("country1Test.csv",teamName="Country1",opposition=c("all"),homeOrAway=c("all"),matchType="Test",plot=FALSE)
#head(df)

# Plot the performance of Country1 Test team  against all teams at all venues
#teamWinLossStatusAtGrounds("country1Test.csv",teamName="Country1",opposition=c("all"),homeOrAway=c("all"),matchType="Test",plot=TRUE)

# Plot the performance of Country1 Test team  against specific teams at home/away venues
#teamWinLossStatusAtGrounds("country1Test.csv",teamName="Country1",opposition=c("Country2","Country3","Country4"),homeOrAway=c("home","away","neutral"),matchType="Test",plot=TRUE)

```

###2c. Test - Plot time lines of wins and losses
```{r}
#plotTimelineofWinsLosses("country1Test.csv",team="Country1",opposition=c("all"), #startDate="1970-01-01",endDate="2017-01-01")
#plotTimelineofWinsLosses("country1Test.csv",team="Country1",opposition=c("Country2","Count#ry3","Country4"), homeOrAway=c("home",away","neutral"), startDate=<start Date> #,endDate=<endDate>)
```

###3a. ODI - Analyzing test performances against opposition
```{r}
#df <- teamWinLossStatusVsOpposition("team1ODI.csv",teamName="Team1",opposition=c("all"),homeOrAway=c("all"),matchType="ODI",plot=FALSE)
#head(df)

# Plot the performance of team1  in ODIs against Sri Lanka, India at all venues
#teamWinLossStatusVsOpposition("team1ODI.csv",teamName="Team1",opposition=c("all"),homeOrAway=c(all"),matchType="ODI",plot=TRUE)

# Plot the performance of Team1 ODI team  against specific teams at home/away venues
#teamWinLossStatusVsOpposition("team1ODI.csv",teamName="Team1",opposition=c("Team2","Team3","Team4"),homeOrAway=c("home","away","neutral"),matchType="ODI",plot=TRUE)
```

###3b. ODI - Analyzing test performances against opposition at different venues
```{r}
#df <- teamWinLossStatusAtGrounds("team1ODI.csv",teamName="Team1",opposition=c("all"),homeOrAway=c("all"),matchType="ODI",plot=FALSE)
#head(df)

# Plot the performance of Team1s in ODIs specific ODI teams at all venues
#teamWinLossStatusAtGrounds("team1ODI.csv",teamName="Team1",opposition=c("all"),homeOrAway=c(all"),matchType="ODI",plot=TRUE)

# Plot the performance of Team1 against specific ODI teams at home/away venues
#teamWinLossStatusAtGrounds("team1ODI.csv",teamName="Team1",opposition=c("Team2","Team3","Team4"),homeOrAway=c("home","away","neutral"),matchType="ODI",plot=TRUE)
```


###3c. ODI - Plot time lines of wins and losses
```{r}
#Plot the time line of wins/losses of Bangladesh ODI team between 2 dates all venues
#plotTimelineofWinsLosses("team1ODI.csv",team="Team1",startDate=<start date> ,endDa#te=<end date>,matchType="ODI")

#Plot the time line of wins/losses against specific opposition between 2 dates
#plotTimelineofWinsLosses("team1ODI.csv",team="Team1",opposition=c("Team2","Team2"), homeOrAway=c("home",away","neutral"), startDate=<start date>,endDate=<end date> ,matchType="ODI")
```


###4a. T20 - Analyzing test performances against opposition
```{r}
#df <- teamWinLossStatusVsOpposition("teamT20.csv",teamName="Team1",opposition=c("all"),homeOrAway=c("all"),matchType="T20",plot=FALSE)
#head(df)

# Plot the performance of Team1 in T20s  against  all opposition at all venues
#teamWinLossStatusVsOpposition("teamT20.csv",teamName="Team1",opposition=c("all"),homeOrAway=c(all"),matchType="T20",plot=TRUE)

# Plot the performance of T20 Test team  against specific teams at home/away venues
#teamWinLossStatusVsOpposition("teamT20.csv",teamName="Team1",opposition=c("Team2","Team3","Team4"),homeOrAway=c("home","away","neutral"),matchType="T20",plot=TRUE)
```

###4b. T20 - Analyzing test performances against opposition at different venues
```{r}
#df <- teamWinLossStatusAtGrounds("teamT20.csv",teamName="Team1",opposition=c("all"),homeOrAway=c("all"),matchType="T20",plot=FALSE)
#head(df)

# Plot the performance of Team1s in ODIs specific ODI teams at all venues
#teamWinLossStatusAtGrounds("teamT20.csv",teamName="Team1",opposition=c("all"),homeOrAway=c(all"),matchType="T20",plot=TRUE)

# Plot the performance of Team1 against specific ODI teams at home/away venues
#teamWinLossStatusAtGrounds("teamT20.csv",teamName="Team1",opposition=c("Team2","Team3","Team4"),homeOrAway=c("home","away","neutral"),matchType="T20",plot=TRUE)
```


###4c. T20 - Plot time lines of wins and losses
```{r}
#Plot the time line of wins/losses of Bangladesh ODI team between 2 dates all venues
#plotTimelineofWinsLosses("teamT20.csv",team="Team1",startDate=<start date> ,endDa#te=<end date>,matchType="T20")

#Plot the time line of wins/losses against specific opposition between 2 dates
#plotTimelineofWinsLosses("teamT20.csv",team="Team1",opposition=c("Team2","Team2"), homeOrAway=c("home",away","neutral"), startDate=<start date>,endDate=<end date> ,matchType="T20")
```

# Key Findings


## Analysis of batsman


##Analysis of bowlers

## Analysis of teams

## Conclusion
Using the above template, analysis can be done for both batsmen and bowlers in Test, ODI and T20. Also analysis of any any team in Test, ODI and T20 against other specific opposition, at home/away and neutral venues can be performed.

Have fun with cricketr!!









